### 2017-06-19 manuscript/manuscript.Rmd
Replace code folder tree with screenshot

```{r git-setup, fig.cap="Setting up Git's configuration using the command line. Notice that for these configuration commands, the current working directory does not matter (we did them in the user's home directory, indicated by \~)."}
knitr::include_graphics("images/git-setup.png")
```

@@

```{r organizing-files, fig.cap = "Organizing one's project helps potential collaborators (including oneself in the future) to quickly and reliably find the correct files. Some bad practices (left panel) include having multiple versions of each file, increasing the potential for e.g. accidentally using the wrong data for the analysis, or forgetting which version was used in the analysis. Better practices (right panel) organize the data to subfolders with meaningful names, and have one file per purpose. These files are then versioned using Git, eschewing the need for multiple files, thereby reducing potential for mistakes."}
knitr::include_graphics("images/git-diagram.png")
```

@@

```{r git-initialize, fig.cap = "Creating and navigating to a folder, and initializing it as a Git repository."}
knitr::include_graphics("images/git-diagram.png")
```

@@

For example, after working for a while on the project, you could have added two files inside well-organized subfolders of the project. The project would like this when viewed with a file explorer:

```bash
git-example/
|-- admin/
    |-- ethics-info.pdf
|-- experiment-1/
    |-- analysis/
        |-- plan_n.R
|-- manuscript/
|-- README
```

>>>>

```{r git-setup, fig.cap="Setting up Git's configuration using the command line. Notice that for these configuration commands, the current working directory does not matter (we did them in the user's home directory, indicated by \\~)."}
knitr::include_graphics("images/git-setup.png")
```

@@

```{r organizing-files, fig.cap = "Organizing one's project helps potential collaborators (including oneself in the future) to quickly and reliably find the correct files. Some bad practices (left panel) include having multiple versions of each file, increasing the potential for e.g. accidentally using the wrong data for the analysis, or forgetting which version was used in the analysis. Better practices (right panel) organize the data to subfolders with meaningful names, and have one file per purpose. These files are then versioned using Git, eschewing the need for multiple files, thereby reducing potential for mistakes."}
knitr::include_graphics("images/project-organization.png")
```

@@

```{r git-initialize, fig.cap = "Creating and navigating to a folder, and initializing it as a Git repository."}
knitr::include_graphics("images/git-initialize.png")
```

@@

For example, after working for a while on the project, you could have added two files inside well-organized subfolders of the project. The project would like Figure \@ref(fig:advanced-project) when viewed with a file explorer:

```{r advanced-project, fig.cap = "A project with more components."}
knitr::include_graphics("images/advanced-project.png")
```
